First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
remove double speak

In order to measure DVCS on $^4$He with a fully exclusive final state, we 
built a specialized radial time projection chamber (RTPC) for detection and identification of
low energy recoiling light nuclei in order to ensure exclusivity of the 
reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.

>>>>

In order to measure DVCS on $^4$He with a fully exclusive final state, we 
built a specialized radial time projection chamber (RTPC) for detection and identification of
low energy recoiling light nuclei. The $^4$He nucleus is an ideal experimental target in this regard, as 
it is light enough to be detected in such a setting, while it
is subject to significant nuclear effects \cite{JSeely} and has rather high 
density.  A helium target leads to another important advantage, as the number of GPDs 
defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case. This significantly
simplifies the interpretation of the data and allows a model independent
extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
end of this letter.
